Democratic Marriage Rates on the Rise: Catching Up with Republicans in the U.S.

### 2023-04-20 outputs/paper/paper.qmd
update title

---
title: "gss marriage politics analysis"
subtitle: "subtitle"
author: 
  - Chloe Thierstein
thanks: "Code and data are available at: https://github.com/cthierst/marital_status_political_affiliation_gss_analysis.git"
date: "April 20, 2023"
date-format: "D MMMM YYYY"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
toc: TRUE
number-sections: TRUE
bibliography: references.bib
---

@@

cleaned_gss_2021$polviews <- 
  factor(cleaned_gss_2021$polviews, 
         levels = c("Extremely Conservative", "Conservative", "Slightly Conservative", "Moderate", "Slightly Liberal", "Liberal", "Extremely Liberal"))

cleaned_gss_2018$polviews <- 
  factor(cleaned_gss_2018$polviews, 
         levels = c("Extremely Conservative", "Conservative", "Slightly Conservative", "Moderate", "Slightly Liberal", "Liberal", "Extremely Liberal"))

cleaned_gss_2016$polviews <- 
  factor(cleaned_gss_2016$polviews, 
         levels = c("Extremely Conservative", "Conservative", "Slightly Conservative", "Moderate", "Slightly Liberal", "Liberal", "Extremely Liberal"))

cleaned_gss_2014$polviews <- 
  factor(cleaned_gss_2014$polviews, 
         levels = c("Extremely Conservative", "Conservative", "Slightly Conservative", "Moderate", "Slightly Liberal", "Liberal", "Extremely Liberal"))
```

>>>>

---
title: "Democratic Marriage Rates on the Rise: Catching Up with Republicans in the U.S."
subtitle: "An Analysis of the 2014-2021 U.S. General Social Survey Data"
author: 
  - Chloe Thierstein
thanks: "Code and data are available at: https://github.com/cthierst/marital_status_politics_gss_analysis.git"
date: "April 20, 2023"
date-format: "D MMMM YYYY"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
toc: TRUE
number-sections: TRUE
bibliography: references.bib
---

@@

cleaned_gss_2021$polviews <- 
  factor(cleaned_gss_2021$polviews, 
         levels = c("Extremely Liberal", "Liberal", "Slightly Liberal",  "Moderate",  "Slightly Conservative","Conservative", "Extremely Conservative"))

cleaned_gss_2018$polviews <- 
  factor(cleaned_gss_2018$polviews, 
         levels = c("Extremely Liberal", "Liberal", "Slightly Liberal",  "Moderate",  "Slightly Conservative","Conservative", "Extremely Conservative"))

cleaned_gss_2016$polviews <- 
  factor(cleaned_gss_2016$polviews, 
         levels = c("Extremely Liberal", "Liberal", "Slightly Liberal",  "Moderate",  "Slightly Conservative","Conservative", "Extremely Conservative"))

cleaned_gss_2014$polviews <- 
  factor(cleaned_gss_2014$polviews, 
         levels = c("Extremely Liberal", "Liberal", "Slightly Liberal",  "Moderate",  "Slightly Conservative","Conservative", "Extremely Conservative"))
